\section*{Acceptance Criteria Games - 99 Balloons - 1}
\subsection*{equipment}
\begin{itemize}
\item a bag of balloons (all the same shape)
\item 20c and 10c coins (or equivalent)
\item string \& ruler, or a flexible ruler
\end{itemize}
\subsection*{before the session}
\begin{enumerate}
\item before the session: blow up a balloon and using the coins to draw two eyes and a nose. Draw a smiling face and optional eyebrows. Make a note of the dimensions of the balloon (perimeter, height, distance between eyes, etc).
\end{enumerate}
\clearpage
\section*{Acceptance Criteria Games - 99 Balloons - 2}
\subsection*{starting the session}
\begin{enumerate}
\item split up the class into teams of about 4
\item give each team a mound of balloons (keep the coins, string and ruler hidden)
\item tell the groups that they need to make me 99 balloons; hold up your pre made balloon and tell them that they need to make theirs like this one. They have 2 minutes. Go!
\end{enumerate}
\subsection*{during an iteration}
\begin{enumerate}
\item don't help
\item keep track of time
\end{enumerate}
\clearpage
\section*{Acceptance Criteria Games - 99 Balloons - 3}
\subsection*{ending an iteration}
\begin{enumerate}
\item examine each balloon compared to the original; discard it if it is even slightly different to original
\item be visibly disappointed in the lack of accurate balloons
\item ask the groups is "making this balloon" was not simple enough?
\item don't tell them any answers, it is there responsibility to ask questions to clarify the intent
\item answer all yes/no questions "should it have two eyes" with a yes/no. Only elaborate when they ask leading questions "should the eyes be of a certain size?"
\end{enumerate}
\clearpage
\section*{Acceptance Criteria Games - 99 Balloons - 4}
\subsection*{length of session}
\begin{enumerate}
\item about 3-4 iterations should be required
\item keep the score on the whiteboard of each team and how many good balloons and how many 'reject' balloons have been made.
\item the group should become frustrated with the constant rejections and will eventually start to ask questions; this is the point
\end{enumerate}
\clearpage
\section*{Acceptance Criteria Games - 99 Balloons - 5}
\subsection*{summary}
\begin{enumerate}
\item have a discussion about asking clarifying questions and the difference between closed (answer is chosen from a set e.g. yes/no) and open (tell me about...) questions
\item also focus on the questions that were asked that confirm what the group already knows vs. uncovers something not yet known by the group.
\item give kudos to anyone asks "why" we are making balloons. An answer is to make children happy (which can lead into a discussion about whether balloons will do that and user feedback)
\end{enumerate}